Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-03 paper/paper.tex
fix table IV

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    Versions (18.07) & 233941 & 6.9.448 & 62.0b9 & 1.10.1 \\
    \midrule
    \jsc{} & - & 11 & - & -  \\
    \veight{} & - & - & - & -  \\
%    \chakra{} & - & - & - & -  \\
    Mozilla & - & 333 & - & -  \\
    Duktape & - & 80 & - & -  \\
    JerryScript & - & 92 & - & -  \\
    JSI & - & 14 & - & -  \\
    Tiny-js & - & 11 & - & -  \\
    \midrule
    Versions (01.08) & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
    \midrule
    \jsc{} & \Fix{10} & 11 & 107 & 157   \\
    \veight{} & 29 & \Fix{0} & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    Mozilla & 741 & 286 & \Fix{178} & 476   \\
    Duktape & 238 & 80 & 202 & 85   \\
    JerryScript & 94 & 89 & 90 & 91   \\
    JSI & 35 & 14 & 14 & 14   \\
    Tiny-js & 11 & 11 & 11 & 11  \\
    \bottomrule 
  \end{tabular}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    \Fix{Versions (01.08)} & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
    \midrule
    \jsc{} & - & 1 & 97 & 147   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 563 & 108 & 0 & 298   \\
    Duktape & 165 & 7 & 129 & 12   \\
    JerryScript & 26 & 21 & 22 & 23   \\
    JSI & 21 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \bottomrule 
  \end{tabular}
\end{table}
